---
title: "SISMID 2021"
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
library(emo)
```




Last update/recompile: `r Sys.time()`

**Site currently under construction. Expect things to not fully work as long as you see this message.**


Welcome to the website for the course/module called [Infectious Diseases, Immunology and Within-Host Models](https://si.biostat.washington.edu/suminst/sismid2021/modules/MD2110), which is part of the [2021 Summer Institute in Statistics and Modeling in Infectious Diseases (SISMID)](https://si.biostat.washington.edu/suminst/sismid). The course is taught by [Andreas Handel](https://www.andreashandel.com/) and [Paul Thomas](https://www.stjude.org/directory/t/paul-thomas.html). 


# Website content

The __Syllabus__ provides a brief overview with a few logistic details.

The __Schedule__ lists the topics, with links to materials. Most of the materials are on a separate site called [Simulation Modeling in Immunology]() which we use as the main, permanent repository for teaching materials related to this course. 

The __Communication__ section provides information on how course communications are planned to happen.

The __Resources__ section contains a listing of external materials. The _Course Resources_ page lists materials used in this course. The _General Resources_ page lists additional materials that are relevant to the course topic and might be of interest. 

The __Glossary__ section provides a (work in progress) glossary with definitions of technical terms.

You have the opportunity to do an optional project. Instructions and detailed information for this are given in the __Project__ section.


# Getting started

Start by looking over the __Syllabus__ and __Schedule__, then __Communication__ and __Resources__. After that, browse through the rest of the content. 

# Notes

We are a _Module_ of SISMID. However, for our purposes, we refer to our module as a _course_ or _class_, and use _module_ for individual segments, which are further divided into _units_. We hope this is not too confusing. 

By default, all links open in the current tab. You'll likely want external ones to open in a separate tab or window. To do so, you can (with most browsers) hold the `Ctrl` button when clicking, or do a right-click and select `open in new tab/window`.


# Contribute

**We welcome contributions in the form of feedback, suggestion for edits/additions, etc. You can either tell us or you can even contribute directly through a GitHub pull request.** (If you don't know what a GitHub pull request is and how you can do that, see the GitHub specific instructions [here](https://andreashandel.github.io/MADAcourse/Exercise_Tidyverse.html). You can ignore the part that talks about the `tidyverse`. You might also want to check out [this brief GitHub introduction](https://andreashandel.github.io/MADAcourse/1d_Github.html)).


# Acknowledgements

This course was developed and is maintained by [Andreas Handel](https://www.andreashandel.com/) and [Paul Thomas](https://www.stjude.org/directory/t/paul-thomas.html).

```{r, results = "asis", echo = FALSE, message = FALSE, warning=FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("coursecontributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{GithubID}](https://github.com/{GithubID})"),
    desc = ifelse(is.na(LastName), link, glue::glue("{FirstName} {LastName} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```


# License

The materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.](https://creativecommons.org/licenses/by-nc-sa/4.0/) Linked and embedded materials are governed by their own licenses. We assume that all external materials used or embedded here are covered under the educational fair use policy. If this is not the case and any material displayed here violates copyright, please let me know and we will remove it. 


  
